Part B-2

### 2024-08-27 msca-pf-part-b2-template.tex
feat: add latex labels to each section

\NewDocumentCommand \ra {} {\raggedright\arraybackslash}

@@

\section{CV of the researcher (indicative length: 5 pages)}

@@

\section{Capacity of the Participating Organisation(s)}

Please provide an overview list of all participating organisations (the
beneficiary and, where applicable, all associated partners) using template
table~\ref{ssc:table1} below, and more detailed information for each of the
participating organisations (using a separate table for each organisation) using
template table~\ref{ssc:table2} below.

@@

\subsection{Template table: Overview of Participating Organisations}
\label{ssc:table1}

Only relevant rows from the table should be kept.

@@

\subsection{Template table: Capacity of the Participating Organisations}
\label{ssc:table2}

@@

\section{Additional ethics information}

@@

\section{Additional information on security screening}

@@

\section{Environmental considerations in light of MSCA Green Charter}

@@

\section{
    Required for Global Fellowships only: Letter(s) of commitment from
    associated partners (hosting of the outgoing phase)}

>>>>

% add your own fancy commands
% \NewDocumentCommand \mycmd { m } {\textbf{#1}}

@@

\section{CV of the researcher (indicative length: 5 pages)}
\label{sc:cv}

@@

\section{Capacity of the Participating Organisation(s)}
\label{sc:organisations}

Please provide an overview list of all participating organisations (the
beneficiary and, where applicable, all associated partners) using template
table~\ref{ssc:organisations:overview} below, and more detailed information for
each of the participating organisations (using a separate table for each
organisation) using template table~\ref{ssc:organisations:capacity} below.

@@

\subsection{Template table: Overview of Participating Organisations}
\label{ssc:organisations:overview}
Only relevant rows from the table should be kept.

@@

\subsection{Template table: Capacity of the Participating Organisations}
\label{ssc:organisations:capacity}

@@

\section{Additional ethics information}
\label{sc:ethics}

@@

\section{Additional information on security screening}
\label{sc:security}

@@

\section{Environmental considerations in light of MSCA Green Charter}
\label{sc:environment}

@@

\section{
    Required for Global Fellowships only: Letter(s) of commitment from
    associated partners (hosting of the outgoing phase)}
\label{sc:commitment_letter}
